DNSKEY Management

### 2012-12-02 paper/paper.tex
Proposed outline
Add command to verify char count
Write some stuff in paper (about DNSSEC...)

\documentclass[a4paper, twocolumn]{scrartcl}

@@

@@

>>>>

\documentclass[a4paper]{scrartcl}

\usepackage{graphicx}

%% Limit: 40000 chars
%% check with `detex paper.tex | wc -c`

@@

\graphicspath{{../figures/}}

\newcommand{\wbjp}{\protect\footnote{Written by Julien Perrochet}}
\newcommand{\wbts}{\protect\footnote{Written by Tobias Schlatter}}

@@

\section{DNSSEC Deployment\wbts}

This section shall expose the current deployment status of DNSSEC.

\subsection{Penetration}

In figure~\ref{fig:dnssec-growth} you can see the development of
deployed, production DNSSEC zones (for the heuristics applied to
determine a production zone, see \cite{secspider, Osterweil09}).

\begin{figure}
  \includegraphics[width=\linewidth]{dnssec-growth}
  \caption{Number of deployed DNSSEC zones by
    SecSpider \cite{secspider}}
  \label{fig:dnssec-growth}
\end{figure}

\subsection{Trust Anchors}

Contrary to the state at writing of \cite{Osterweil09}, the DNS
root-zone is signed since July 15, 2010 \cite{root-dnssec} and hence
serves as the global trust anchor.

\section{Operations\wbjp}
\subsection{3Rs}
\subsection{Single admin}
\subsection{Multi admin}
\subsection{Disabling}

\section{Case-Study: Switzerland (\texttt{ch.} Zone)\wbts}
According to a query on \cite{secspider}, the \verb|ch.| TLD zone is signed and
fully veryfiable from the root zone anchor. The validity period of a
zone signing key is 37 days \cite{switch10}.
